R Notebook

### 2022-11-15 Scripts/data_cleaning.Rmd
Minor text edits + fixing NAs in inc.termlimit.num (0s for parliamentary elections)
Adding event counts and protest sizes from Mass Mobilization dataset (note: quality checks still needed)

@@

nelda3 <- nelda2 %>% merge(massmob, by = "country_id_year")
```

Cutting out protests before elections for nelda 3, 
```{r}
nelda3 <- nelda3 %>% filter(protest_mdy >= election_mdy)
```

@@

```{r}
nelda2.sub <- nelda2 %>% filter(v2x_regime == 1 | v2x_regime == 2)
```

@@

##Size
ecav <- ecav %>% mutate(ParticipantNumber = ifelse(ParticipantNumber == -99, NA, ParticipantNumber))
size_data <- ecav %>% group_by(NeldaID) %>% summarize(median.participants = median(ParticipantNumber))

ecav.pre <- ecav.pre %>% mutate(ParticipantNumber = ifelse(ParticipantNumber == -99, NA, ParticipantNumber))
size_data_pre <- ecav.pre %>% group_by(NeldaID) %>% summarize(median.participants.pre = median(ParticipantNumber))

@@

nelda2.sub <- nelda2.sub %>% mutate(antigov.violence = ifelse(is.na(antigov.violence)==T, 0, antigov.violence))
nelda2.sub <- nelda2.sub %>% mutate(n.events.post = ifelse(is.na(n.events.post)==T, 0, n.events.post))
nelda2.sub <- nelda2.sub %>% mutate(d.events.num = ifelse(is.na(d.events.num)==T, 0, d.events.num))
nelda2.sub <- nelda2.sub %>% mutate(median.participants = ifelse(is.na(median.participants)==T, 0, median.participants))

@@

```{r}
nelda3 <- nelda3 %>% mutate(protests.postelex = ifelse(protests == 1 & protesterdemand1 == "political behavior, process", 1, 0))

nelda3 <- nelda3 %>% mutate(protests.postelex.quant = ifelse(protests.postelex == 1, protestnumber, 0))
```

Cutting out closed autocracies and liberal democracies

```{r}
nelda3.sub <- nelda3 %>% filter(v2x_regime == 1 | v2x_regime == 2)
```

@@

>>>>

                                                  v2ex_elechog,

@@

#nelda3 <- nelda2 %>% merge(massmob, by = "country_id_year")

nelda3 <- nelda %>% dplyr::select(ccode, country, year, electionid, election_mdy)
nelda3 <- nelda3 %>% mutate(election_year = year)
nelda3 <- massmob %>% left_join(nelda3, by = c("ccode", "year")) #Nelda3 is in progress, need to figure out a) if needed, b) how to include pre-election and post-election mobilization
```

Cutting out protests before elections for nelda 3, 
```{r}
#Add electionid to the year before the election and year after (so that grouping variable can capture those protests if needed)
nelda3 <- nelda3 %>% group_by(ccode) %>% mutate(election_date_upcoming = as_date(ifelse(is.na(election_year)==F, election_mdy, 
                                                  ifelse(is.na(election_year)==T & is.na(lead(election_mdy))==F,
                                                                          lead(election_mdy), NA))))

nelda3 <- nelda3 %>% group_by(ccode) %>% mutate(election_date_lagged = as_date(ifelse(is.na(election_year)==F, election_mdy,                                                         ifelse(is.na(election_year)==T & is.na(lag(election_mdy))==F, lag(election_mdy), NA))))

## Now filter by date of protest

# Steps:
  #1) Remove rows where election_upcoming and election_lagged are both NA. 
  #2) This results in a dataframe with only election years +-1 year; create interval variables (lagged and leading days between protest and election)
  #3 Filter to cases that are six months before to 3 months after election (i.e 180 days and 90 days)

nelda3.sub <- nelda3 %>% filter(is.na(election_date_upcoming)==F | is.na(election_date_lagged) == F)

nelda3.sub <- nelda3.sub %>% mutate(protest_preelex_interval = ifelse((election_mdy - protest_mdy) >0, (election_mdy-protest_mdy), NA))

nelda3.sub <- nelda3.sub %>% mutate(protest_postelex_interval = ifelse((election_mdy - protest_mdy) <= 0, (protest_mdy - election_mdy), NA))

nelda3.sub <- nelda3.sub %>% group_by(ccode) %>% filter(protest_preelex_interval <= 180 | protest_postelex_interval <= 90)

# Next step is to aggregate needed variables (participants) by electionid
```

Aggregating participant variables
```{r}

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(participants_category == "", NA, 
                                            ifelse(participants_category == "50-99", 1, 
                                            ifelse(participants_category == "100-999", 2,
                                            ifelse(participants_category == "1000-1999", 3,
                                            ifelse(participants_category == "2000-4999", 4,
                                            ifelse(participants_category == "5000-10000", 5,
                                                   6)))))))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "100s", 2, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "1000s", 4, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== ">50", 1, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "50", 1, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "1000", 3, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "50+", 1, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "100", 2, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "10000", 5, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "2000", 4, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "200", 2, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "300", 2, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "500", 2, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "3000", 4, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "100+", 2, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "5000", 5, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "20000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "10000s", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "150", 2, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "400", 2, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "hundreds", 2, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "30000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "100000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "15000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "1500", 3, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "> 50", 1, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "4000", 4, participants_category_ordered))  ## Stopping here; all other categories have fewer than 20 observations. Beginning second stopping rule:

## Second rule: collect all observations greater than 10,000

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "hundreds of thousands", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "<20000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "> 40000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "> 42000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== ">35000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== ">40000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== ">50000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "1000000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "110000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "14059", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "16000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "18000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "24000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "250000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "30000+", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "35000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "36000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "5000-50000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "55000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "650000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "> 10000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "1000000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "13000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "500000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== ">15000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== ">20000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "14000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "400000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "Tens of thousands", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== ">100000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "150000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "20000+", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "60000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "90000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "10000+", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "100000s", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "200000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "80000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== ">10000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "70000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "80000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "40000", 6, participants_category_ordered))

nelda3.sub <- nelda3.sub %>% mutate(participants_category_ordered = ifelse(is.na(participants_category_ordered) == T & participants== "25000", 6, participants_category_ordered))

#nelda3.sub <- nelda3.sub %>% group_by(electionid) %>% 
```

Remove post-election protests unrelated to election

```{r}
nelda3.sub <- nelda3.sub %>% filter(protest_mdy < election_mdy | (protest_mdy >= election_mdy & str_detect(notes, regex(pattern = "election*|vot*|ballot*", ignore_case = T))))
```

Getting grouped summarize for number and size
```{r}
nelda3.sub.pre <- nelda3.sub %>% filter(protest_mdy < election_mdy)
nelda3.sub.post <- nelda3.sub %>% filter(protest_mdy >= election_mdy)

count_data_mm_pre <- nelda3.sub.pre %>% group_by(electionid) %>% summarize(n.events.massmob.pre = sum(protestnumber))
count_data_mm_post <- nelda3.sub.post %>% group_by(electionid) %>% summarize(n.events.massmob.post = sum(protestnumber))

size_data_mm_pre <- nelda3.sub.pre %>% group_by(electionid) %>% summarize(median.participants.pre = median(participants_category_ordered, na.rm = T))
size_data_mm_post <- nelda3.sub.post %>% group_by(electionid) %>% summarize(median.participants.post = median(participants_category_ordered, na.rm = T))

@@

```{r}
nelda2.sub <- nelda2 %>% filter(v2x_regime == 1 | v2x_regime == 2) #Note that coding scheme for electoral democracies allows for "some degree of fraud and irregularities but these did not in the end affect the outcome" (v2elfrfair, which is a component of v2x_regime) 
```

@@

##Size
ecav <- ecav %>% mutate(ParticipantNumber = ifelse(ParticipantNumber == -99, NA, ParticipantNumber))
size_data <- ecav %>% group_by(NeldaID) %>% summarize(median.participants = median(ParticipantNumber, na.rm = T))

ecav.pre <- ecav.pre %>% mutate(ParticipantNumber = ifelse(ParticipantNumber == -99, NA, ParticipantNumber))
size_data_pre <- ecav.pre %>% group_by(NeldaID) %>% summarize(median.participants.pre = median(ParticipantNumber, na.rm = T))

@@

nelda2.sub <- nelda2.sub %>% mutate(antigov.violence = ifelse(is.na(antigov.violence)==T, 0, antigov.violence))
nelda2.sub <- nelda2.sub %>% mutate(n.events.post = ifelse(is.na(n.events.post)==T, 0, n.events.post))
nelda2.sub <- nelda2.sub %>% mutate(d.events.num = ifelse(is.na(d.events.num)==T, 0, d.events.num))
#nelda2.sub <- nelda2.sub %>% mutate(median.participants = ifelse(is.na(median.participants)==T, 0, median.participants))

@@

```{r}
#nelda3 <- nelda3 %>% mutate(protests.postelex = ifelse(protests == 1 & protesterdemand1 == "political behavior, process", 1, 0))

#nelda3 <- nelda3 %>% mutate(protests.postelex.quant = ifelse(protests.postelex == 1, protestnumber, 0))
```

@@

## Merge data from nelda3.sub with nelda2.sub

```{r}
##Combined post data together, then pre data, then both
mm_data_post_comb <- left_join(count_data_mm_post, size_data_mm_post, by = "electionid")
mm_data_pre_comb <- left_join(count_data_mm_pre, size_data_mm_pre, by = "electionid")

mm_data_comb <- left_join(mm_data_pre_comb, mm_data_post_comb, by = "electionid")

mm_data_comb <- mm_data_comb %>% rename(NeldaID = electionid)

nelda2.sub <- nelda2.sub %>% left_join(mm_data_comb, by = "NeldaID")  ## Double check to make sure this joining works
